Measuring Perceptions and Preferences for Meritocracy

### 2021-01-06 docs/paper.Rmd

kable(tab.inv, col.names = col.nam, align = "l",
      booktabs=TRUE,format = table_format,escape = FALSE,
      caption = "Multiple Group meassurement invariance for Perceptions and Preferences for Meritocracy") %>% 
  kable_styling(full_width = FALSE) %>%
  footnote(general = footnote, footnote_as_chunk = T)
```

@@

>>>>

kable(tab.inv, col.names = col.nam, align = "l",
      booktabs=TRUE,format = table_format,escape = FALSE,
      caption = "Multiple Group meassurement invariance for Perceptions and Preferences for Meritocracy") %>% 
  kable_styling(full_width = FALSE,latex_options = "HOLD_position") %>%
  footnote(general = footnote, footnote_as_chunk = T)
```

@@

```{r fcloads-inv, echo=FALSE}
load(file = "../output/tables/tb.fact-f02.RData")
tb.foot <- paste0("Standardized factor loadings using DWLS estimator ; CFI = Comparative fit index (scaled); RMSEA = Root mean square error of approximation (scaled)")
tb.fm02<- kable(tb.fm2,escape = FALSE,align = "lcccc",col.names = tb.col, caption = tb.caption, booktabs = T,linesep = "",format = table_format) %>% 
          kable_styling(full_width = table_format2,latex_options = c("hold_position"), position = "center",font_size = 9) %>% 
          add_header_above(header = c(" "=1,"Factor loadings"= 4)) %>%
          row_spec(row = 8,hline_after = TRUE) %>%
          add_indent(c(9:12)) %>% 
          footnote(general =tb.foot ,footnote_as_chunk = T);tb.fm02
```
